LIONFISH: an expLoratory Interactive tOol for dyNamic visualization and identiFicatIon multidimenSional mecHanisms

### 2024-09-27 manuscript.tex
quotes to proper double quotes

The Austrian Vacation Activities dataset comprises responses from 2,961 adult tourists who spent their holiday in Austria during the 1997/98 season. Participants were asked to evaluate the importance of 27 different activities during their vacation. The survey categorized responses based on four levels of importance: ``totally important", ``mostly important", ``a bit important", and ``not important". For analysis, the responses were binarized: a value of 1 was assigned if the activity was rated as ``totally important", and a value of 0 if any of the other categories were selected. The survey was conducted by the Europäisches Tourismus Institut GmbH at the University of Trier and focused exclusively on tourists who did not stay in the country's capital cities.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_pre.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset, with manually adjusted projections. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Changing the projection axes of ``going to a spa", ``museums", ``sightseeing" and ``using health facilities" reveals the preferences and overlap of clusters 1 and 3.}
    \label{fig:winter_cl7_pre}
\end{figure}

@@

At first, hierarchical clustering using Ward's method \citep{murtagh2014ward} and the Jaccard index was applied to the features. The resulting dendrogram is shown in Figure \ref{fig:aus_feature_clustering}. Based on this clustering, \( k = 15 \) clusters were identified, and generally, only one representative feature from each cluster was selected for further analysis. Clusters containing unpopular activities, such as ``Adventure", which only had 42 participants, were discarded. The cluster containing popular features like ``Beach", ``Swimming", ``ScenicWalks", ``Markets", ``Sightseeing", ``Friends", ``Pubs", ``BBQ", ``Shopping", ``Eating", ``EatingHigh", ``Movies," and ``Relaxing" was treated differently. Multiple features from this cluster were retained to preserve as much information as possible. After feature selection, the observations were reclustered using k-means with \( k = 15 \).

>>>>

The Austrian Vacation Activities dataset comprises responses from 2,961 adult tourists who spent their holiday in Austria during the 1997/98 season. Participants were asked to evaluate the importance of 27 different activities during their vacation. The survey categorized responses based on four levels of importance: ``totally important'', ``mostly important'', ``a bit important'', and ``not important". For analysis, the responses were binarized: a value of 1 was assigned if the activity was rated as ``totally important'', and a value of 0 if any of the other categories were selected. The survey was conducted by the Europäisches Tourismus Institut GmbH at the University of Trier and focused exclusively on tourists who did not stay in the country's capital cities.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_pre.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset, with manually adjusted projections. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Changing the projection axes of ``going to a spa'', ``museums'', ``sightseeing" and ``using health facilities" reveals the preferences and overlap of clusters 1 and 3.}
    \label{fig:winter_cl7_pre}
\end{figure}

@@

At first, hierarchical clustering using Ward's method \citep{murtagh2014ward} and the Jaccard index was applied to the features. The resulting dendrogram is shown in Figure \ref{fig:aus_feature_clustering}. Based on this clustering, \( k = 15 \) clusters were identified, and generally, only one representative feature from each cluster was selected for further analysis. Clusters containing unpopular activities, such as ``Adventure'', which only had 42 participants, were discarded. The cluster containing popular features like ``Beach'', ``Swimming'', ``ScenicWalks'', ``Markets'', ``Sightseeing'', ``Friends'', ``Pubs'', ``BBQ'', ``Shopping'', ``Eating'', ``EatingHigh'', ``Movies'', and ``Relaxing'' was treated differently. Multiple features from this cluster were retained to preserve as much information as possible. After feature selection, the observations were reclustered using k-means with \( k = 15 \).
